---
title: "Exercise 7"
author: 'Ben Hanowell'
date: "`r Sys.Date()`"
output: html_document
---

## Setup

```{r setup}
# Install pacman
if (!require("pacman")) install.packages("pacman")
# p_load function loads packages if installed, or install then loads otherwise
pacman::p_load(dplyr, knitr, kableExtra, readr)
```

## Data collection {.unnumbered}

```{r}
CHLasfrRR <- readRDS(url("https://github.com/hanowell/uwsoc533a-exercise-07/blob/main/data/CHLasfrRR.rds?raw=true"))
CHLbirthsRR <- readRDS(url("https://github.com/hanowell/uwsoc533a-exercise-07/blob/main/data/CHLbirthsRR.rds?raw=true"))
```

## About the data {.unnumbered}

**You've just loaded three data sets:**

* **`CHLasfrRRbo` gives the period age-specific fertility rate (`ASFR`) as well as the parity-specific ASFR (`ASFR[parity]`) by `Age` by one-year age group for Chile in 1992**
* **`CHLbirthsRRbo` gives you the period number of births (`Total`) as well as the parity-specific number of births (`B[parity]`) by `Age` by one-year age group for Chile in 1992**

## Compute the Total Fertility Rate (TFR) from the data provided

**1 point**

```{r}

```

## TFR vs. Total Marital Fertility Rate (TMFR)

**With reference to their formal definitions, explain why the total marital fertility rate (TMFR) is assumed to be greater than or equal to the TFR in Bongaarts' proximate determinants framework, and what this implies for the numerical bounds of the coefficient of sexual union. (1 point)**

**Answer below:**



## Compute the crude birth rate (CBR) from the data provided

**1 point**

```{r}

```


## TFR vs. crude birth rate (CBR)

**Compare the TFR to the CBR and explain the difference between them with respect to the age structure of fertility in Chile in 1992. (1 point)**